|

### 2020-08-25 paper.Rmd
mapping out application section, and synonyms for reverse

@@

In this work we address the piling in low-dimensional linear projections, which is in particular a barrier for viewing high-dimensional distributions with tour methods [@As85,@BCAH05]. Tours show interpolated sequences of low-dimensional projections of the data. When exploring a dataset with a tour we can discover features that are only visible from specific viewing angles. However, these features may easily be hidden if most of the observations pile up near the center, with a large fraction of the plotting canvas showing only outlying points. To counteract the effect, we introduce a radial transformation that zoomes in near the center of the distribution.

@@

To offset this effect, we introduce a radial transformation that redistributes the projected points, such that equal volume in the original ($p$-dimensional) space is projected onto equal area in a 2-dimensional projection. Note that it is straightforward to generalize this for $d$-dimensional projections by mapping onto equal $d$-dimensional volume instead.

@@

```{r circles, fig.cap="Rescaled equidistant concentric circles, for $p=2, 3, 10, 100$. The circles remain equidistant for $p=2$ where no transformation is performed, and get pushed out towards the edge as $p$ increases.", out.width="75%", fig.align = "center"}

@@

## Image classification

@@

>>>>

<!-- Reverse, redistribute, counteract, offset, rescale, radial transformation -->

@@

In this work we address the piling in low-dimensional linear projections, which is in particular a barrier for viewing high-dimensional distributions with tour methods [@As85,@BCAH05]. Tours show interpolated sequences of low-dimensional projections of the data. When exploring a dataset with a tour we can discover features that are only visible from specific viewing angles. However, these features may easily be hidden if most of the observations pile up near the center, with a large fraction of the plotting canvas showing only outlying points. To reverse the effect, we introduce a radial transformation that zoomes in near the center of the distribution.

@@

To reverse this effect, we introduce a radial transformation that redistributes the projected points, such that equal volume in the original ($p$-dimensional) space is projected onto equal area in a 2-dimensional projection. Note that it is straightforward to generalize this for $d$-dimensional projections by mapping onto equal $d$-dimensional volume instead.

@@

```{r circles, fig.cap="Equidistant concentric circles, for $p=2, 3, 10, 100$, illustrating the radial transformation. The circles remain equidistant for $p=2$ where no transformation is performed, and get pushed out towards the edge as $p$ increases.", out.width="75%", fig.align = "center"}

@@

Four applications of the sage tour are shown here, which illustrate the benefit of using the reverse transformation for examining data using a tour: single cell RNA-seq, classifying hand-sketched images, comparing physics experiments, and the classical pollen data which is used to illustrate the effect of parameter choices.

## scRNA

- *Analysis purpose*:

Something about usual analysis methods too, and how this helps to complement these.
- *Summary of data pre-processing*:
- *What is learned from the sage tour that is hidden in a regular tour*:

## Classifying hand-sketches

@@

## Comparing physics experiments: PDFSense

## Tuning the parameters: Pollen
